%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
	\textbf{\Huge \scshape Ayush Mishra} \\ \vspace{1pt}
	\small +91-7899059160 $|$ \href{mailto:piymis6@gmail.com}{\underline{piymis6@gmail.com}} $|$ 
	\href{https://linkedin.com/in/piymis}{\underline{linkedin.com/in/piymis}} $|$
	\href{https://piymis.com/}{\underline{piymis.com}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Georgia Insititute of Technology}{Atlanta, USA}
{Master of Science in Computer Science;  GPA: 4.0/4.0}{2024}

\resumeSubheading
{Delhi Technological University}{Delhi, India}
{Bachelor of Technology in Electronics and Communication;  GPA: 8.1/10.0}{2015}
\resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Media.net}{Bangalore, India}
{Lead Software Engineer}{July 2022 - Present}
\resumeItemListStart
\resumeItem{Developed Open Backend (OBE) components to handle shopping and booking transactions for Hotel IT \& Rail web services distribution platform.}
\resumeItemListEnd


\resumeSubheading
{Goibibo \& MakeMyTrip }{Bangalore, India}
{Lead Software Engineer \& Senior Software Engineer II}{October 2019 - July 2022}
\resumeItemListStart		
\resumeItem{Leading the backend team to build and maintain a scalable platform for hoteliers with a B2B application which powers the Hotels and Homestays to millions of customers on both MakeMyTrip \& Goibibo.}
\resumeItem{Developed microservices \& functionalities such as Images \& Video, Amenities, Policy \& House rules, Services \& Notices, How to reach property, Surveys, User Generated Content (Review, Rating, Replies) for the above application.}
\resumeItem{Developed features such as Property Onboarding/Listing, Property Layout Modeling, Import listing from other channels such as Airbnb, etc. for the MakeMyTrip homestay mobile application.}
\resumeItem{Developed a full-stack web application using Django, DRF, MongoDB, MySQL, and Docker for the moderation of Images \& Videos.}
\resumeItem{Developed a finite state machine for the state management of on-boarded hotel \& homestay properties. The data is persisted in MySQL and subsequently pushed to ElasticSearch for indexing and Kafka for client consumption.}
\resumeItem{Developed the architecture to support the integration of multi-vendor content (Synxis, Derbysoft, OYO \& Amazon) to power hotel content.}
\resumeItem{Optimizing application performance metrics such as \textbf{response time, latency, and throughput} by optimizing the application code and database queries through various APM metrics targeting the SLA of 99.99\% availability}
\resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

\resumeSubheading
{Amadeus Labs}{Bangalore, India \& Nice, France}
{Senior Software Engineer \& Software Engineer}{July 2015 - October 2019}
\resumeItemListStart
\resumeItem{Developed Open Backend (OBE) components to handle shopping and booking transactions for Hotel IT \& Rail web services distribution platform.}
\resumeItem{Developed web application, REST API \& python library for managing passenger record data (PNR).}
\resumeItem{Built a python library integrating the centralized data logging service for the pushing, fetching, and parsing of logs.}
\resumeItemListEnd


\resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart
\resumeProjectHeading
{\textbf{Developed an interactive weather application on the Android OS to fetch and show the weather and climatic conditions of any area.} $|$ \emph{C, pthreads}}{}
          
\resumeProjectHeading
{\textbf{Developed an application on the Android OS to play the xylophone music instrument.} $|$ \emph{C++14, gRPC, and Protocol Buffers.}}{}
\resumeItemListStart
\resumeItem{Designed and implemented a distributed file system (DFS) with a weakly consistent synchronization system to manage cache consistency between multiple clients and a single server. }
\resumeItemListEnd
      
\resumeProjectHeading
{\textbf{Virtual CPU Scheduler and memory coordinator} $|$ \emph{C, KVM, libvirt}}{}
\resumeItemListStart
\resumeItem{Implemented a hypervisor CPU scheduler and memory manager using libvirt API.}
\resumeItemListEnd
      
\resumeProjectHeading
{\textbf{MapReduce implementation using gRPC} $|$ \emph{C++14, gRPC, and Protocol Buffers.}}{}
\resumeItemListStart
\resumeItem{Implemented a threadpool of workers, partitioning the input data, scheduling the program’s execution across a set of workers, handling worker failures, and using gRPC for master-worker communication.}
\resumeItemListEnd
      
     
\resumeSubHeadingListEnd



%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
	\small{\item{
		\textbf{Languages}{:}\hspace{16pt}{C++, Java, JavaScript, TypeScript, Python, SQL, HTML, CSS} \\
		\textbf{Technologies}{: Elasticsearch, AWS, Snowflake, Spring Boot, Spring Web MVC framework, JPA, Hibernate} \\
		\hspace{71pt}{React, Git, Oracle DB2, Android Development} \\
		\textbf{Others}{: }\hspace{30pt}{Git, Docker, AWS, GCP, Jenkins, Grafana, Sumologic, Scalyr, NewRelic} \\
	}}
\end{itemize}


% --------Awards ------------ 
\section{Awards \& Recognition}
\begin{itemize}[leftmargin=0.15in, label={}]
	\small{\item{
			\resumeItemListStart
			\resumeItem{Selected for Go Share Program at Visa to work with the Payment System Risk team for three months as UI developer.}
			\resumeItem{Participated in the Data Product Development hackathon, our team got an honorable mention for our idea.}
			\resumeItem{Scored in the top 1 percentile in JEE Main examination.}
			\resumeItem{Received LIC Student of the Year award 2013 in high school.}
			\resumeItemListEnd
	}}
\end{itemize}
%-------------------------------------------
\end{document}